### 2018-10-16 tex/model.tex
fzw revision

\begin{figure*}
    \centering
	\includegraphics[width=0.85\textwidth]{fig/model_basic}
	\caption{\color{blue}FRQ Model}
    \label{fig:model_basic}
    \vspace{-1em}
\end{figure*}

@@

\subsection{The FRQ Model}\label{model_overview}
The current distributed parallel computing frameworks mostly use \textit{Directed acyclic graphs} (DAGs) to describe computation logic. A shuffle phase is required between each adjacent DAG computation phase. In order to better analyze the relationship between the computation phase and the shuffle phase, we propose FRQ model. After quantifying computing and I/O resources, FRQ model is able to describe different resource scheduling strategies. For convenience, we introduce FRQ model by taking a simple MapReduce as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. FRQ model has five input parameters:
\begin{enumerate}
	\item Input Data Size \((D)\): The data size of the computation phase.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This conversion rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase using the current computation resources. The number of rounds depends on the current computation resources and the settings of the computation job. Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the Map phase consists of 200 map tasks. Then we need 4 rounds of computation to complete the Map phase.
    \item Computation Speed \((V_{i})\): 
    The computation speed for each computation phase. The computation speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
    Transmission speed during shuffle. Shuffle speed depends on Network and storage device bandwidth.
\end{enumerate}

We can calculate the execution time of each phase of the job with these five parameters. Obviously, the total execution time of job in this case is the sum of the Map phase time and Reduce phase time:
\begin{equation}
\label{equation_Tjob}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Reduce}
\end{aligned}
\end{equation}
Map phase time depends on input data size and Map computation speed:
\begin{equation}
\label{equation_Tmap}
\begin{aligned}
    T_{Map} &= {{\frac{D}{V_{Map}}}}
\end{aligned}
\end{equation}
The Reduce phase time formula is as follows:
\begin{equation}
\label{equation_Treduce}
\begin{aligned}
    T_{Reduce} &= \frac{D \times R}{V_{Reduce}} + K \times T_{P\_Shuffle}
\end{aligned}
\end{equation}
\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time, and \(K \times T_{P\_Shuffle}\) represents the calculated overhead. \(K\) is empirical value. The overhead depends on the parallel time of shuffle phase and the Reduce phase.The parallel time is denoted by \(T_{P\_Shuffle}\). And the total time of shuffle phase is represented by \(T_{Shuffle}\). Because the computation of the Reduce phase relies on the data transfer results of the Shuffle phase, a portion of the computation in the Reduce phase need to wait for the transfer results. The overhead is caused by these waiting. The FRQ model uses K to indicate the extent of the waiting.

@@

For shuffle-heavy computing jobs, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\). Improving IO speed is a effective way to reduce shuffle time. Another optimization method is to use the idle IO resources in the Map phase for pre-fetching (see Figure \ref{fig:model_basic}). Both of the above methods can effectively reduce \(T_{P\_Shuffle}\). When using FRQ model to describe a computation job, we can easily analyze the resource scheduling strategy of the computation framework. Different computing frameworks may use different resource scheduling strategies. FRQ model can evaluate the scheduling strategies of these computing frameworks and help us optimize them.

@@

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_original}
				\caption{\color{blue}Full Serial MapReduce}
				\label{fig:model_original}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_hadoop}
				\caption{\color{blue}Hadoop MapReduce}
				\label{fig:model_hadoop}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}FRQ Model with Different Scheduling Strategies}
		\label{fig:model_strategies}
	\end{minipage}
\end{figure}

FRQ model can describe a variety of resource scheduling strategies. First, we analyze a naive scheduling strategy. As shown in Figure \ref{fig:model_original}, FRQ model describes a MapReduce job that is fully serially executed. The parallel time of shuffle phase and the Reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\). Therefore, the overhead of the Reduce phase is 0. But since shuffle and computation are serial execution, the total execution time of job becomes longer:
\begin{equation}
\label{equation_Tjob2}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
\end{aligned}
\end{equation}
Obviously, this is an inefficient scheduling strategy. No computing framework uses this scheduling method. Due to serialization, the IO resource is idle during the Reduce phase and Map phase. The scheduling strategy is naive and has a lot of room for optimization.

Figure \ref{fig:model_hadoop} shows the scheduling strategy of Hadoop MapReduce. In Hadoop MapReduce, Shuffle phase and Reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of Reduce phase will increase (see equation \ref{equation_Treduce}). Because the Shuffle phase and the computation phase are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}). The execution time of Shuffle phase is hidden in the Reduce phase. This scheduling strategy is much more efficient than the one in Figure 1. However, after analyzing this model, we found that the IO resource in the Map phase is idle. This scheduling strategy can be optimized.

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_scache1}
				\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
				\label{fig:model_scache1}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_scache2}
				\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
				\label{fig:model_scache2}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}FRQ Model with SCache}
		\label{fig:model_scache}
	\end{minipage}
\end{figure}

Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4). SCache starts pre-fetching and pre-scheduling in the Map phase. This scheduling strategy can make better use of resources and avoid IO resources being idle in the Map phase. According to the design of SCache pre-fetching, we found that using FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

\begin{itemize}
    \item 
    \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1}): 
	The meaning of \(V_{Map} \times R\) is the speed at which shuffle data is generated. The meaning of the inequality is that the speed of generating shuffle data(\(V_{Map} \times R\)) is greater than or equal to the shuffle speed(\(V_{Shuffle}\)). When the Round1 of the Map phase ends, the SCache starts shuffling data until the end of the shuffle phase. Due to shuffle speed is slower, the shuffle phase is uninterrupted. SCache transmit the shuffle data generated in the last round of Map phase during the Reduce phase. Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase:
	\begin{equation}
		\label{equation_Tpshuffle1}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N}
		\end{aligned}
	\end{equation}

    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2}): 
	When the speed of generating shuffle data (\(V_{Map} \times R\)) is less than the shuffle speed (\(V_{Shuffle}\)), SCache needs to wait for shuffle data to be generated. As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each Round. Thus \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the Map phase:
	\begin{equation}
		\label{equation_Tpshuffle2}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} \times \frac{1}{N}
		\end{aligned}
	\end{equation}
\end{itemize}

% After analyzing the above two situations, we figure out the formula for \(T_{P\_Shuffle}\):
% \begin{equation}
%     \label{equation_Tpshuffle}
%     \begin{aligned}
%     T_{P\_Shuffle} &=
%         \begin{cases} 
%         T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N} & , V_{Map} \times R \ge V_{Shuffle} \\ 
%         T_{Shuffle} \times \frac{1}{N} & , V_{Map} \times R < V_{Shuffle}
%         \end{cases}
%     \end{aligned}
% \end{equation}
% If the shuffle speed is slow(\(V_{Map} \times R \ge V_{Shuffle}\)), SCache transmit the shuffle data generated in the last round of Map phase during the Reduce phase. Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase.

% If the shuffle speed is fast (\(V_{Map} \times R < V_{Shuffle}\)), \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the Map phase.

Compared to the original Hadoop MapReduce resource scheduling strategy, Hadoop MapReduce with SCache reduces \(T_{P\_Shuffle}\) and thus lessens \textit{Reduce Time} (\(T_{Reduce}\)). This is how pre-fetching optimizes the total execution time of job.

@@

\subsection{Model Verification}\label{model_verification}
In order to verify FRQ model, we run experiment on two environments. The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Section \ref{stepup}. Another environment is in our lab. Out lab environment has 4 nodes and each nodes has 128GB and 32 CPUs. To simplify the calculation of the FRQ model, we use Hadoop MapReduce as framework (only three phases: \textit{Map, Shuffle,} and \textit{Reduce}) and Terasort as experimental application. We deployed Hadoop with SCache and without SCache on both environments.

Table \ref{table1} shows the calculational results of FRQ model in the lab environment. Workload is from 16 GB to 64 GB. \(D\) and \(N\) are set according to the application parameters. \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are calculated based on experimental results. K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the Reduce phase in the case of SCache. The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively. In the case of SCache, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache1} (\(V_{Map} \times R \ge V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}. In the case of Legacy, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}). \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\). The formula of \(Error\) is:
\begin{equation}
	\label{equation_error}
	\begin{aligned}
		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
	\end{aligned}
\end{equation}

>>>>

\begin{figure*}
    \centering
	\includegraphics[width=0.85\textwidth]{fig/model_basic}
	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
    \label{fig:model_basic}
    \vspace{-1em}
\end{figure*}

@@

\subsection{The FRQ Model}\label{model_overview}
The current distributed data parallel computing frameworks mostly use \textit{Directed acyclic graphs} (DAGs) to describe computation logic. A shuffle phase is required between each adjacent DAG computation phase. In order to better analyze the relationship between the computation phase and the shuffle phase, we propose FRQ model. After quantifying computing and I/O resources, FRQ model is able to describe different resource scheduling strategies. For convenience, we introduce FRQ model by taking a simple MapReduce job as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. FRQ model has five input parameters:
\begin{itemize}
	\item Input Data Size \((D)\): The data size of the computation phase.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This conversion rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase using the current computation resources. The number of rounds depends on the current computation resources and the settings of the computation job. Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the map phase consists of 200 map tasks. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
    The computation speed for each computation phase. The computation speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
    Transmission speed during shuffle. Shuffle speed depends on Network and storage device bandwidth.
\end{itemize}

We can calculate the execution time of each phase of the job with these five parameters. As shown in Figure \ref{fig:model_basic}, in full parallel mapReduce, the total execution time of a job is the sum of the map phase time and reduce phase time:
\begin{equation}
\label{equation_Tjob}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Reduce}
\end{aligned}
\end{equation}
map phase time depends on input data size and Map computation speed:
\begin{equation}
\label{equation_Tmap}
\begin{aligned}
    T_{Map} &= {{\frac{D}{V_{Map}}}}
\end{aligned}
\end{equation}
The reduce phase time formula is as follows:
\begin{equation}
\label{equation_Treduce}
\begin{aligned}
    T_{Reduce} &= \frac{D \times R}{V_{Reduce}} + K \times T_{P\_Shuffle}
\end{aligned}
\end{equation}

We use \(T_{P\_Shuffle}\) to represent the overlap time between shuffle phase and reduce phase. \(T_{Shuffle}\) represents the total time of shuffle phase. 
The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and \(K \times T_{P\_Shuffle}\) represents the computing overhead. \(K\) is an empirical value. 
Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase need to wait for the transfer results. The overhead is caused by these waiting. The FRQ model uses K to indicate the extent of the waiting.

@@

For shuffle-heavy computing jobs, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\). Improving I/O speed is a effective way to reduce shuffle time. Another optimization method is to use the idle I/O resources in the map phase for pre-fetching (see Figure \ref{fig:model_basic}). Both of the above methods can effectively reduce \(T_{P\_Shuffle}\). When using FRQ model to describe a computation job, we can easily analyze the resource scheduling strategy of the computation framework. Different computing frameworks may use different resource scheduling strategies. FRQ model can evaluate the scheduling strategies of these computing frameworks and help us optimize them.

@@

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_original}
				\caption{\color{blue}Full Serial MapReduce}
				\label{fig:model_original}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_hadoop}
				\caption{\color{blue}Half Parallel MapReduce}
				\label{fig:model_hadoop}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
		\label{fig:model_strategies}
	\end{minipage}
\end{figure}

The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a naive scheduling strategy. As shown in Figure \ref{fig:model_original}, FRQ model describes a MapReduce job that is fully serially executed. The overlap time between shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\). Therefore, the overhead of the reduce phase is 0. But since shuffle and computation are serial execution, the total execution time of a job is different from the above:
\begin{equation}
\label{equation_Tjob2}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
\end{aligned}
\end{equation}
Apache Spark uses this scheduling strategy by default. Due to serialization, the I/O resource is idle during the reduce phase and map phase. The scheduling strategy is simple and has a lot of room for optimization.

Figure \ref{fig:model_hadoop} shows one of the optimization methods. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase will increase (according to equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}). The execution time of shuffle phase is hidden in the reduce phase. This scheduling strategy is used by Hadoop MapReduce. After analyzing this model, we believe that this strategy will be more efficient than the above serial strategy in the same situation. Meanwhile, we found that the I/O resource in the map phase is still idle. This scheduling strategy can be optimized.

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_scache1}
				\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
				\label{fig:model_scache1}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_scache2}
				\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
				\label{fig:model_scache2}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
		\label{fig:model_scache}
	\end{minipage}
\end{figure}

Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources. We intuitively think that we can also overlap shuffle phase one and map phases. We implemented this idea with SCache.
Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4). SCache starts pre-fetching and pre-scheduling in the map phase. This scheduling strategy can make better use of resources and avoid the I/O resource being idle in the map phase. According to the design of SCache pre-fetching, we found that using FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

\begin{enumerate}
    \item 
    \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1}): 
	The meaning of \(V_{Map} \times R\) is the speed at which shuffle data is generated. The meaning of the inequality is that the speed of generating shuffle data(\(V_{Map} \times R\)) is greater than or equal to the shuffle speed(\(V_{Shuffle}\)). When the Round1 of the map phase ends, the SCache starts shuffling data until the end of the shuffle phase. Due to shuffle speed is slower, the shuffle phase is uninterrupted. SCache transmit the shuffle data generated in the last round of map phase during the reduce phase. Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase:
	\begin{equation}
		\label{equation_Tpshuffle1}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N}
		\end{aligned}
	\end{equation}

    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2}): 
	When the speed of generating shuffle data (\(V_{Map} \times R\)) is less than the shuffle speed (\(V_{Shuffle}\)), SCache needs to wait for shuffle data to be generated. As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each Round. Thus \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the map phase:
	\begin{equation}
		\label{equation_Tpshuffle2}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} \times \frac{1}{N}
		\end{aligned}
	\end{equation}
\end{enumerate}

% After analyzing the above two situations, we figure out the formula for \(T_{P\_Shuffle}\):
% \begin{equation}
%     \label{equation_Tpshuffle}
%     \begin{aligned}
%     T_{P\_Shuffle} &=
%         \begin{cases} 
%         T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N} & , V_{Map} \times R \ge V_{Shuffle} \\ 
%         T_{Shuffle} \times \frac{1}{N} & , V_{Map} \times R < V_{Shuffle}
%         \end{cases}
%     \end{aligned}
% \end{equation}
% If the shuffle speed is slow(\(V_{Map} \times R \ge V_{Shuffle}\)), SCache transmit the shuffle data generated in the last round of map phase during the reduce phase. Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase.

% If the shuffle speed is fast (\(V_{Map} \times R < V_{Shuffle}\)), \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the map phase.

Compared to the original Hadoop MapReduce resource scheduling strategy, Hadoop MapReduce with SCache reduces \(T_{P\_Shuffle}\) and thus lessens \(T_{Reduce}\). This is how pre-fetching optimizes the total execution time of a job.

@@

\subsection{Model Verification}\label{model_verification}
In order to verify FRQ model, we run experiment on two environments. The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Section \ref{stepup}. Another environment is in our lab. Out lab environment has 4 nodes and each nodes has 128GB and 32 CPUs. To simplify the calculation of the FRQ model, we use Hadoop MapReduce as framework and Terasort as experimental application. We deployed Hadoop with SCache and without SCache on both environments.

Table \ref{table1} shows the calculational results of FRQ model in the lab environment. Workload is from 16 GB to 64 GB. \(D\) and \(N\) are set according to the application parameters. \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are calculated based on experimental results. K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase in the case of SCache. The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively. In the case of SCache, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache1} (\(V_{Map} \times R \ge V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}. In the case of Legacy, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}). \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\). The formula of \(Error\) is:
\begin{equation}
	\label{equation_error}
	\begin{aligned}
		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
	\end{aligned}
\end{equation}
